Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-04-14 manuscript/supplementaryRW.Rmd
added landclim report to supplementary

-   Lexer MJ, Hönninger K (2001) A modified 3D-patch model for spatially
    explicit simulation of vegetation composition in heterogeneous
    landscapes. For Ecol Manag 144:43--65.
    doi:10.1016/S0378-1127(00)00386-8

-   Seidl R, Lexer MJ, Jäger D, Hönninger K (2005) Evaluating the
    accuracy and generality of a hybrid patch model. Tree Physiol
    25:939--951. doi:10.1093/treephys/25.7.939

-   Woltjer M, Rammer W, Brauner M, Seidl R, Mohren GMJ, Lexer MJ (2008)
    Coupling a 3D patch model and a rockfall module to assess rockfall
    protection in mountain forests. J Environ Manag 87:373--388.
    doi:10.1016/j.jenvman.2007.01.031

@@

@@

The most complete reference resource for the LandClim model and
regeneration module is:

@@

@@

@@

@@

@@

@@

>>>>

-   Lexer MJ, Hönninger K (2001) A modified 3D-patch model for spatially
    explicit simulation of vegetation composition in heterogeneous
    landscapes. For Ecol Manag 144:43--65.
    [doi:10.1016/S0378-1127(00)00386-8](doi:10.1016/S0378-1127(00)00386-8){.uri}

-   Seidl R, Lexer MJ, Jäger D, Hönninger K (2005) Evaluating the
    accuracy and generality of a hybrid patch model. Tree Physiol
    25:939--951. <doi:10.1093/treephys/25.7.939>

-   Woltjer M, Rammer W, Brauner M, Seidl R, Mohren GMJ, Lexer MJ (2008)
    Coupling a 3D patch model and a rockfall module to assess rockfall
    protection in mountain forests. J Environ Manag 87:373--388.
    <doi:10.1016/j.jenvman.2007.01.031>

@@

Olalla Díaz-Yáñez, Harald Bugmann

@@

We use the LandClim version 2.0, which calculates forest dynamics at a
decadal time step. The complete reference resource for the LandClim
model and regeneration module are:

-   SCHUMACHER, S., H. BUGMANN, AND D. J. MLADENOFF. (2004). "Improving
    the formulation of tree growth and succession in a spatially
    explicit landscape model" Ecological Modelling 180: 175-194.

-   SCHUMACHER,  S. AND H. BUGMANN. (2006). "The relative importance of
    climatic effects, wildfires and management for future forest
    landscape dynamics in the Swiss Alps" Global Change Biology 12:
    1435-1450.

-   SCHUMACHER, S., B. REINEKING, J. SIBOLD, AND H. BUGMANN. (2006).
    "Modeling the impact of climate and vegetation on fire regimes in
    mountain landscapes" Landscape Ecology 21: 539-554.

-   Manual available on the model web page:
    <https://ites-fe.ethz.ch/openaccess/products/landclim>

@@

Climate inputs for LandClim are at monthly temporal resolution. We used
monthly climate from the CHELSA dataset provided in the protocol using
temperature and precipitation variables. -during the simulations, we
sampled the climate time series randomly.

@@

We used the soil quality provided to infer the Available Water Holding
Capacity needed in LandClim. We assigned 8 cm for soil quality one and
25 cm for soil quality five and interpolated the values for the other
categories linearly between the two extremes.

@@

We used the altitude and soil information provided in the protocol to
create the different landscapes, one per site. However, each landscape
created per site had no slope, altitude, or aspect variation.

@@

We simulated forest dynamics only considering the 11 species proposed in
the protocol: *Fagus sylvatica, Picea abies, Abies alba, Carpinus
betulus, Tilia cordata, Acer pseudoplatanus, Betula* spp.*, Fraxinus
excelsior, Quercus* spp.*, Alnus glutinosa,* and *Pinus sylvestris.*

@@

We simulate forest dynamics from bare ground for each of the sites. We
prepared landscapes of 250x250m without topographical elevation for each
of the sites. The simulations we run from bare ground to 2000 years and
the samples were taken from the year 2000. On the regeneration module,
we use a background probability of 0.001, a dispersal mode based on the
formulation random asymmetric, and the same establishment probability
for all the species included in the simulation of 0.9.

@@

We estimated the outputs based on a sample of 25 random cells every ten
years from 2000 to 4000 of the simulation for one simulation per site,
providing 200 samples per site.
